Cleaning our own Dust: Simulating and Separating Galactic Dust Foregrounds with Convolutional Networks

### 2018-08-09 PAPER/main.tex
Update main.tex
minor edits to section 2

%\title{Simulating Galactic Dust with Deep Convolutional Generative Adversarial Networks}
\title{Cleaning our own Dust: Simulating and Separating Galactic Dust Foregrounds with Convolutional Networks}
\author{K. Aylor}
\affiliation{Department of Physics, University of California, Davis, CA, USA 95616}
\author{ M. Haq}
\author{L. Knox }
\affiliation{Department of Physics, University of California, Davis, CA, USA 95616}

@@

A Deep Convolutional Generative Adversarial Network (DCGAN) is a form of unsupervised machine learning which attempts to model a generating function which can create samples from a desired distribution. The DCGAN architecture was first introduced in the seminal paper, \cite{goodfellow14}.
A DCGAN consists of two sub-models, a discriminator and a generator, each with their own sets of weights that are to be optimized.
The discriminator is optimized to detect samples from $P$ and the generator is optimized to create samples from $P$.
During the training process the discriminator is shown labeled samples from $P$ and from the generator, as the discriminator improves at detecting samples from $P$ the generator must improve at creating samples belonging to $P$ to minimize its own loss function. Training proceeds until the generator's output distribution has converged to $P$.
For the case of generating $N\times M$ pixel images, the generator $\rm{G}(z)$ maps $z$, a random vector from $Z$, to $P$ in $\mathbb{R}^{N\times M}$. 
The generator then allows one to perform importance sampling as $Z$ is a distribution where it is known how to produce samples i.e. a Gaussian distribution.

>>>>

%\title{Simulating Galactic Dust with Deep Convolutional Generative Adversarial Networks}
\title{Cleaning our own Dust: Simulating and Separating Galactic Dust Foregrounds with Convolutional Networks}
\author{K. Aylor}
\affiliation{Department of Physics, University of California, Davis, CA, USA 95616}
\author{ M. Haq}
\author{L. Knox }
\affiliation{Department of Physics, University of California, Davis, CA, USA 95616}
\author{Y. Hezaveh }
\affiliation{Department of Physics, Stanford University, Stanford, CA, USA 94305}

@@

A Generative Adversarial Network (GAN) is a form of unsupervised machine learning which attempts to model a generating function which can create samples from a desired distribution \citep{goodfellow14}. 
A GAN consists of two sub-models, a discriminator and a generator, each with their own sets of weights that are to be optimized.
The discriminator is optimized to detect samples from $P$, the distribution which we desire to emulate, and the generator is optimized to create samples from $P$.
During the training process the discriminator is shown labeled samples from $P$ and from the generator, as the discriminator improves at detecting samples from $P$ the generator must improve at creating samples belonging to $P$ to minimize its own loss function. Training proceeds until the generator's output distribution has converged to $P$.
For the case of generating $N\times M$ pixel images a Deep Convolutional GAN (DCGAN), first presented in \cite{radford15}, has proven to be effective. In this architecture the generator $\rm{G}(z)$ maps $z$, a random vector from $Z$, to $P$ in $\mathbb{R}^{N\times M}$ through a series of upsamplings via convolutions. 
The generator then allows one to perform importance sampling as $Z$ is a distribution where it is known how to produce samples i.e. a Gaussian distribution.
